Country-Level Impact of Education on Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing

Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out. It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded there may be a small cultural effect in attitudes toward start-up activities.

Rather than trying to trace cultural patterns at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" [@OECD2009]. Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and staff attitudes.

>>>>

Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out. It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded that there might be a small cultural effect in attitudes toward start-up activities.

Rather than trying to trace cultural patterns at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" [@OECD2009]. Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and their personnel's attitudes.
